Look, we can do something

### 2024-11-11 paper.tex
Table of ranges

>>>>

Summarizing, we can divide pores into three groups by the quality of
clusterization (see \cref{tab:ranges}).
\begin{table*}[!htp]
  \centering
  \begin{tabular}{|c|c|}
    \hline
    \highlight{Awesomeness} & Comment \\
    \hline
    < 0.1 & Virtually many different pores connected by thin chords \\
    \hline
    0.1 - 0.6 & Pores which can be divides into subpores \\
    \hline
    > 0.6 & Well-clusterized pores \\
    \hline
  \end{tabular}
  \caption{Different values of \highlight{awesomeness} and their meaning.}
  \label{tab:ranges}
\end{table*}
